---
title: "Lab 6"
author: "Jaxon Stuhr"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Example of a rank-based text

We'll make our own samples using pseudo-random generator

```{r}
set.seed(1414)
gp_1 = sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 = sample.int(30, size = 15, replace = TRUE)
```

```{r}
hist(gp_1)

hist(gp_2)
```

Try a t-test

```{r}
t.test(gp_1, gp_2)
```

What is the meaning of this p-value?

If the samples were drawn from popus w the same mean (same popu), there's a 19.8% chance that we would have found samples at least this different by random chance... Thus we cannot reject the null that they are drawn from popus w same mean.

Now let's compare to rank-based test

## Mann Whitney U unpaired Rank-based test

```{r}
mwu = wilcox.test(gp_1, gp_2)
```
What is the meaning of this p-value?

If the samples were drawn from popus w the same rank (same popu), there's a 28% chance that we would have found samples at least this different by random chance... Thus we cannot reject the null that they are drawn from popus w same rank. rank ~ median

Thus there is no significant difference in ranks/medians between groups 1 and 2