---
title: "Lab 6"
author: "Jaxon Stuhr"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Example of a rank-based text

We'll make our own samples using pseudo-random generator

```{r}
set.seed(1414)
gp_1 = sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 = sample.int(30, size = 15, replace = TRUE)
```

```{r}
hist(gp_1)

hist(gp_2)
```

Try a t-test

```{r}
t.test(gp_1, gp_2)
```

What is the meaning of this p-value?

If the samples were drawn from popus w the same mean (same popu), there's a 19.8% chance that we would have found samples at least this different by random chance... Thus we cannot reject the null that they are drawn from popus w same mean.

Now let's compare to rank-based test

## Mann Whitney U unpaired Rank-based test

```{r}
mwu = wilcox.test(gp_1, gp_2)
```
What is the meaning of this p-value?

If the samples were drawn from popus w the same rank (same popu), there's a 28% chance that we would have found samples at least this different by random chance... Thus we cannot reject the null that they are drawn from popus w same rank. rank ~ median

Thus there is no significant difference in ranks/medians between groups 1 and 2

## Linear Regressions

Simple linear regression (single dependent variable, single indep variable)

```{r}
# Make exploratory plot of penguin body mass (y axis) vs flipper length (x axis)

ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point() + 
  geom_smooth(method = "lm") #don't add w/o being able to explain
```

Find a linear regression model using ordinary least squares describing the relationship between flipper length and body mass for these penguins

3 pieces:
 - What type of model?
 - What is relationship to model? [ DV(IVs) ]
 - What us the data that's used to create model?
 
```{r}
penguin_lm = lm(body_mass_g ~ flipper_length_mm, data = penguins)
```

What does it mean !?

 body mass = 49.69 x flipper length - 5780.83
 
 penguin_lm$coefficients returns [b,m]
 
### broom package

returns model outputs as tidy data frames

```{r}
penguin_lm_tidy = broom::tidy(penguin_lm)

penguin_lm_tidy

```

```{r}
extract_eq(model = penguin_lm, use_coefs = TRUE)
```


